%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-Advisors: Prof. Janusz Fr\k{a}czek \& D.Sc. Marek Wojtyra} % Institute
    {Development of Kinematic Analysis Tool Using Absolute Coordinates - Warsaw University of Technology} % Title
    {Warsaw, Poland} % Location
    {Oct. 2024 - Jan. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developed a kinematic analysis tool using absolute coordinates for a general case planar multi-body system in MATLAB environment.}
        \item {Tested the implementation against results obtained from \emph{MSC Adams} simulation software.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advisor: Dr inż. Paweł Maci\k{a}g} % Institute
    {Kinematics Analysis and Trajectory Planning of a 6 DoF Serial Manipulator} % Title
    {Warsaw, Poland} % Location
    {Feb. 2022 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Derived the analytical solution of the inverse kinematics of the robot arm.}
        \item {Performed both task space and joint space trajectory planning for a simple pick and place task.}
        \item {Tested the performance of the implementation on the actual hardware.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advisor: prof. dr hab. in{\.z}. Cezary Zieli{\.n}ski} % Institute
    {Controller Design Specification for a 6-DOF Serial Manipulator with a Two-State Gripper Endowed with Visual Perception} % Title
    {Warsaw, Poland} % Location
    {Feb. 2022 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Determined the internal structure of the agent and appropriate sampling rates of the agents’ subsystems.}
        \item {Specified the general behavior of the virtual effectors and receptors.}
        \item {Defined the data structures (buffers) within the control subsystem of the agent and the transition functions as well as terminal conditions governing the behaviours of the agent.}
        \item {Determined the structure of the \emph{FSM} of the control subsystem invoking the defined behaviours.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
